The effects of varying depth in cosmic shear surveys

### 2019-10-11 paperdraft.tex
corrected more things

\begin{figure*}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
\end{subfigure}
\caption{Recovered cosmological parameters for a variable-depth (Observed) and uniform-depth (Reference) KiDS-$450$-like (left) and KiDS-$15\,000$-like survey (right). The KiDS-$450$-like figure was computed using the covariance matrix of H18. For the KiDS-$15\,000$-like survey, we divided the one of H18 by 30. This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements. Therefore, this figure constitutes a conservative estimate of this effect for Euclid and LSST. Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
\label{fig:mcmc_results}
\end{figure*}

@@

As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties for a KiDS-$450$-like survey. To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a KiDS-$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KiDS-450. Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$. As our modified covariance-matrix does not account for the factor of $\sim 4$ expected increase in galaxy number density for LSST and Euclid , we note that this likely to be a lower estimate for the significance of the effect.
 We note that even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.   Placing a selection criteria on redshift estimation success will therefore lead to depth variations in the source galaxy sample. While the data from LSST will be practically free of variations in depth after 10 years of observations, the first few years data will include significant depth variation. The impact may be even stronger than the KiDS-like analysis presented here as the multi-band KiDS depth variation was minimised using seeing-dependent data acquisition. This is in contrast to the seeing-agnostic multi-band cadence of LSST.

>>>>

\begin{figure*}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_kids.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{images/mcmc_euclid.pdf}
\end{subfigure}
\caption{Recovered cosmological parameters for a variable-depth (Observed) and uniform-depth (Reference) KiDS-$450$-like (left) and KiDS-$15\,000$-like survey (right). The KiDS-$450$-like figure was computed using the covariance matrix of H18. For the KiDS-$15\,000$-like survey, we divided the one of H18 by 30. This approximately accounts for the increased survey area of next-generation experiments, but does not factor in the increased number density and better shape measurements. Therefore, this figure constitutes a conservative estimate for the effect of variable depth for Euclid and LSST. Both figures were computed using a fiducial cosmology of $\Omega_{\rm{m}}=0.25$ and $\sigma_8 = 0.85$.}
\label{fig:mcmc_results}
\end{figure*}

@@

As can be seen in Fig.~\ref{fig:mcmc_results}, the impact of varying depth is insignificant compared to the uncertainties for a KiDS-$450$-like survey. To get a rough estimate for the impact on future surveys, we divide our covariance-matrix by a factor of 30 to model a KiDS-$15\,000$-like survey, which approximately accounts for the increased survey area of LSST and Euclid with respect to KiDS-450. Here, the impact on $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ is significant at the level of approximately $1\sigma$. As our modified covariance-matrix does not account for the factor of $\sim \! 4$ expected increase in galaxy number density for LSST and Euclid, we note that this likely to be a lower estimate for the significance of the effect.
 Even though Euclid is a space-based mission, and therefore will not suffer from variable atmospheric effects, the key photometric redshift measurement uses data from several ground-based surveys, including KiDS.   Placing a selection criteria on redshift estimation success will therefore lead to depth variations in the source galaxy sample. While the data from LSST will be practically free of variations in depth after 10 years of observations, the first few years data will include significant depth variation. The impact may be even stronger than the KiDS-like analysis presented here as the multi-band KiDS depth variation was minimised using seeing-dependent data acquisition. This is in contrast to the seeing-agnostic multi-band cadence of LSST.
